Heuristics and Really Hard Instances for Subgraph Isomorphism Problems

### 2016-01-14 paper/paper.tex
More outline
Typso

\title{Heuristics and Really Hard Instances for Subgraph Isomorphism Problems}
\author{Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
    Research Council [grant number EP/K503058/1]} \and Patrick Prossser \and James Trimble \\
University of Glasgow, Glasgow, Scotland \\
c.mccreesh.1@research.gla.ac.uk}

@@

?? Explain bottom row of \cref{figure:induced}, and give way of calculating it. The key point is
that depending upon where we are, changes to one of the two terms has more effect in the equation.

>>>>

\title{Heuristics and Really Hard Instances for Subgraph Isomorphism Problems}
\author{Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
    Research Council [grant number EP/K503058/1]} \and Patrick Prosser \and James Trimble \\
University of Glasgow, Glasgow, Scotland \\
c.mccreesh.1@research.gla.ac.uk}

@@

?? Explain bottom row of \cref{figure:induced}, and give way of calculating it. The key point is
that depending upon where we are, changes to one of the two terms has more effect in the equation.
Note how sharp and well-defined this is.
